\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[scale=0.9, bottom=2.5cm]{geometry}
\usepackage{paralist}
\usepackage{lmodern}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\moderncvcolor{blue}
\moderncvstyle{casual}

\name{Kyle}{Reinholdtsen}
\title{Software Engineer}  
\mobile{(425)~215-2474}
\address{Greater Seattle Area}{WA}{}
\email{kyle@reinholdtsen.com}
\social[linkedin][linkedin.com/in/kyle-reinholdtsen-306849223/]{Kyle Reinholdtsen}
\homepage{kyle.reinholdtsen.com}

\begin{document}

\makecvtitle

\vspace{-1.5em}

\section{Experience}

\cventry{08/2025 -- Present}{Full Stack Software Engineer}{Citizen Mint}{Remote}{}{
  \begin{compactitem}
    \item Developed a full-stack web application using Vue (Nuxt), FastAPI, PostgreSQL, and AWS.
    \item Architected and built an internal payment distribution system that processed \$500k+ in investor returns with 0 payment errors over 3 months.
    \item Streamlined admin workflows including CSV upload/download, rich text and media content management, and PDF document generation, reducing operation time from hours to minutes.
    \item Implemented secure authentication features including MFA (email/SMS via Cognito + Lambda) and JWT-based inactivity timeouts.
    \item Delivered responsive and accessible investment listing pages with client-side filtering for 10+ offerings.
  \end{compactitem}
}

\cventry{01/2022 -- 03/2023}{Software Engineer}{Husky Robotics Club, University of Washington}{Seattle}{}{
  \begin{compactitem}
    \item Developed the mission control web application for Husky Robotics, a student engineering team, to operate the team’s rover using JavaScript, React, and Redux.
    \item Designed and implemented a custom WebSocket-based JSON messaging protocol to enable real-time, bidirectional communication between the mission control website and the rover.
    \item Visualized live rover telemetry through dashboards displaying position, power, velocity, and camera feeds.
    \item Rendered a 3D model of the rover using React Three Fiber, dynamically updated from telemetry data.
  \end{compactitem}
}

\section{Education}

\cventry{06/2021 -- 12/2023}{B.S. Computer Science \& Engineering}{University of Washington}{Seattle}{}{}
\cvitem{}{\textbf{GPA:} 3.88 (Cum Laude)}

\section{Projects}

\cventry{}{Paintle}{\href{https://paintle.net}{\textnormal{paintle.net}}}{\href{https://github.com/KyleR56/paintle-front-end}{\textnormal{GitHub}}}{}{
  \begin{compactitem}
    \item Designed and shipped a responsive Wordle-inspired puzzle game in Angular, designed for seamless play on both desktop and mobile.
    \item Deployed a fully serverless architecture on AWS using S3 (frontend), Lambda (backend logic), API Gateway (routing), and DynamoDB (storage), achieving <$200\,$ms cold-start latency and \$0 backend cost under typical usage.
    \item Integrated secure authentication via Google OAuth 2.0 and JWTs, incorporating best practices such as short-lived tokens, RS256 asymmetric signing, and validation of token audience and issuer.
  \end{compactitem}
}

\cventry{}{MCQuest}{\href{https://github.com/mc-quest/mc-quest}{\textnormal{GitHub}}}{}{}{
  \begin{compactitem}
    \item Developed a custom Minecraft server to support a multiplayer RPG with questing, combat, and character progression.
    \item Collaborated with a 5-person team using Agile practices including structured requirements planning, sprint-based development, weekly standups, and CI/CD pipelines to ensure quality and fast iteration.
    \item Engineered backend systems in Java for handling in-game mechanics such as physics calculations, skill behavior, item interactions, and data persistence.
  \end{compactitem}
}

\section{Skills}

\cvitem{Languages}{TypeScript, Python, Java}
\cvitem{Frontend}{Vue (Nuxt), React, Tailwind CSS}
\cvitem{Backend}{Node.js, Express, FastAPI, PostgreSQL}
\cvitem{Cloud}{AWS (ECS, RDS, S3, Lambda, API Gateway, SNS)}
\cvitem{DevOps \& Tools}{Git, GitHub Actions (CI/CD), Docker}

\end{document}
